\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-06-05 forwards-and-backwards.tex
more brackets to fix
.

\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
    \label{lem:eta_projections_tightness}
	For each $f \in C^{\infty}_{b}(\overline{\IR}^d)$, 
the collection of processes
$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
for $N = 1, 2, \ldots$ is tight
as a sequence of c\`adl\`ag, real-valued processes.
\end{lemma}
\begin{proof}
The Aldous-Rebolledo criterion (Theorem~\ref{thm:aldous_rebolledo})
applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
of equation~\eqref{eqn:eta_f_mgale_decomp}, tells us
that it suffices to show that for each $T>0$,
(a) for each fixed $0\leq t\leq T$, the sequence $\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight,
and (b) for any sequence of stopping times $\tau_N$ bounded by $T$,
and for each $\nu > 0$, there exist $\delta > 0$ and $N_0 > 0$ such that 
\begin{gather}
        \label{eqn:eta_projections_goal1}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\left|
            \int_\tau^{\tau + t}
            \int_{\IR^d}
            \left\{
                \gamma(x, \eta^N_s) B^\theta_f(x, \eta^N_s)
                + f(x) F(x, \eta^N_s)
            \right\} 
            \eta^N_s(dx)
            ds
        \right|> \nu \right\}
        < \nu ,
    \\ \text{and} \qquad
        \label{eqn:eta_projections_goal2}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\big|
        [M^{N}(f)]_{\tau + t} 
            - [M^{N}(f)]_\tau \big|
        > \nu
    \right\}
    < \nu.
\end{gather}
Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
so we focus on the remaining conditions.

@@

Similarly,
\begin{align*}
    &
 \big|   [M^{N}(f)]_{\tau + t} 
        - [M^{N}(f)]_\tau \big|
    \\ & \qquad =
  \Big|  \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \int_{\IR^d} f^2(y) r(y, \eta^N_s) q_\theta(x, dy)
            +
            \mu_\theta(x, \eta^N_s) f^2(x)
        \right\}
        \eta^N_s(dx)
    ds \Big|
    \\ & \qquad =
   \Big| \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \left(
                2 f^2(x) r(x, \eta^N_s)
                +
                B^\theta_{f^2}(x, \eta^N_s)
            \right)
            -
            f^2(x) \frac{F(x, \eta^N_s)}{ \theta}
        \right\}
        \eta^N_s(dx)
    ds\Big| ,
\end{align*}
and so using the fact that $\theta/N \to \alpha < \infty$,
an argument entirely analogous to 
that for \eqref{eqn:eta_projections_goal1}
yields a $\delta_2$ for which \eqref{eqn:eta_projections_goal2} is
satsified. Taking $\delta=\min\{\delta_1,\delta_2\}$, the result follows.

@@

    Since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
    the Burkholder-Davis-Gundy inequality
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c_\theta(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & \le
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C_2 e^{C_1 T} ,
    \end{align*}
    for a constant $C_2$ which is finite
    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.

>>>>

\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
    \label{lem:eta_projections_tightness}
	For each $f \in C^{\infty}_{b}(\overline{\IR}^d)$, 
the collection of processes
$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
for $N = 1, 2, \ldots$ is tight
as a sequence of c\`adl\`ag, real-valued processes.
\end{lemma}
\begin{proof}
The Aldous-Rebolledo criterion (Theorem~\ref{thm:aldous_rebolledo})
applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
of equation~\eqref{eqn:eta_f_mgale_decomp}, tells us
that it suffices to show that for each $T>0$,
(a) for each fixed $0\leq t\leq T$, the sequence $\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight,
and (b) for any sequence of stopping times $\tau_N$ bounded by $T$,
and for each $\nu > 0$, there exist $\delta > 0$ and $N_0 > 0$ such that 
\begin{gather}
        \label{eqn:eta_projections_goal1}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\left|
            \int_\tau^{\tau + t}
            \int_{\IR^d}
            \left\{
                \gamma(x, \eta^N_s) B^\theta_f(x, \eta^N_s)
                + f(x) F(x, \eta^N_s)
            \right\} 
            \eta^N_s(dx)
            ds
        \right|> \nu \right\}
        < \nu ,
    \\ \text{and} \qquad
        \label{eqn:eta_projections_goal2}
    \sup_{N > N_0}
    \sup_{t \in [0, \delta]}
    \IP\left\{\big|
        \langle M^{N}(f) \rangle_{\tau + t} 
            - \langle M^{N}(f) \rangle_\tau \big|
        > \nu
    \right\}
    < \nu.
\end{gather}
Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
so we focus on the remaining conditions.

@@

Similarly,
\begin{align*}
    &
 \big|   \langle M^{N}(f) \rangle_{\tau + t} 
        - \langle M^{N}(f) \rangle_\tau \big|
    \\ & \qquad =
  \Big|  \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \int_{\IR^d} f^2(y) r(y, \eta^N_s) q_\theta(x, dy)
            +
            \mu_\theta(x, \eta^N_s) f^2(x)
        \right\}
        \eta^N_s(dx)
    ds \Big|
    \\ & \qquad =
   \Big| \int_{\tau}^{\tau + t}
        \frac{\theta}{N}
        \int_{\IR^d}
        \left\{
            \gamma(x, \eta^N_s)
            \left(
                2 f^2(x) r(x, \eta^N_s)
                +
                B^\theta_{f^2}(x, \eta^N_s)
            \right)
            -
            f^2(x) \frac{F(x, \eta^N_s)}{ \theta}
        \right\}
        \eta^N_s(dx)
    ds\Big| ,
\end{align*}
and so using the fact that $\theta/N \to \alpha < \infty$,
an argument entirely analogous to 
that for \eqref{eqn:eta_projections_goal1}
yields a $\delta_2$ for which \eqref{eqn:eta_projections_goal2} is
satsified. Taking $\delta=\min\{\delta_1,\delta_2\}$, the result follows.

@@

    As in the proof of Lemma~\ref{lem:eta_compact_containment},
    the Burkholder-Davis-Gundy inequality,
    \citet{barlow/jacka/yor:1986},
    and the fact that $\sqrt{x} \le 1 + x$ for $x \ge 0$
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c_\theta(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & \le
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C_2 e^{C_1 T} ,
    \end{align*}
    for a constant $C_2$ which is finite
    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.
